Post-replication citation patterns in psychology: Four case studies

### 2021-07-19 manuscript/manuscript.Rmd
Update manuscript.Rmd

# Materials, data, and analysis code availability
All data, materials, and analysis scripts related to this study are publicly available on the Open Science Framework (https://osf.io/w8h2q/). To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code using knitr (Xie, 2017) and papaja (Aust & Barth, 2020), and is available in a Code Ocean container (https://doi.org/10.24433/CO.4225975.v2) which re-creates the software environment in which the original analyses were performed.

>>>>

# Materials, data, and analysis code availability
All data, materials, and analysis scripts related to this study are publicly available on the Open Science Framework (https://osf.io/w8h2q/). To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code using knitr (Xie, 2017) and papaja (Aust & Barth, 2020), and is available in a Code Ocean container (https://doi.org/10.24433/CO.4225975.v3) which re-creates the software environment in which the original analyses were performed.
